\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer} % Job title
    {Facebook} % Organization
    {Menlo Park, CA} % Location
    {July 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {placeholder}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern (Part Time)} % Job title
    {Toast} % Organization
    {Boston, MA} % Location
    {Feb. 2019 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built the infrastructure and automation pipeline for Android's Espresso test framework, enabling developers to use Espresso for UI tests instead of the current, significantly slower, custom Appium-based framework. Used Jenkins, AWS EC2, and Genymotion Cloud for scalability.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Drizly} % Organization
    {Boston, MA} % Location
    {May. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a re-designed onboarding workflow with automated Salesforce integration for new customers to streamline the onboarding process for both customers and account managers.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Facebook} % Organization
    {Menlo Park, CA} % Location
    {Jan. 2018 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped migrate the Instagram Django web server to perform parallel IO operations and handle concurrent requests within each worker process to reduce latency and increase capacity as the app scales with users and features.}
		\item {Created a framework to safely predict the performance and correctness of worker processes handling concurrent requests from a production environment. Preemptively caught and fixed regressions related to increased cpu instructions, caching, and global state contamination.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Toast} % Organization
    {Boston, MA} % Location
    {Jan. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a microservice, database schema, and related web pages to manage customer accounts --- 50,000+ created within the first two months.}
		\item {Designed and helped implement a second microservice to build the foundation for upcoming payment features and reduce technical debt.}
		\item {Enhanced the audit tool to query real-time data from restaurants' Android devices, proactively resolving customers' configuration bugs.}
      \end{cvitems}
    }

  \cventry
    {Programming Mentor, TA} % Job title
    {CSTUY Hacking Sessions} % Organization
    {New York, NY} % Location
    {Sept. 2014 - Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught programming concepts to high school students using Java and Processing while providing input for lesson plans and project ideas.}
      \end{cvitems}
    }    
\end{cventries}
